---
title: "Week 3 practice"
author: "Ash S"
date: "February 6, 2018"
output:
  html_document :
    toc: yes
    toc_depth: '4'
  pdf_document :
      keep_text: yes
      toc: yes
      toc_depth: 1
geometry: right=2.5 in
---

## R Objects

R has five atomic (basic) classes of objects:

* Character
* Numeric (real numbers)
* Integer #
* Complex
* Logic (TRUE/FALSE)

## EXAMPLES (THE <- IS THE ASSIGNMENT OPERATOR)
```{r}
NAME<-"Rockville"
X<-sqrt(2)
N<-8L
Z<-3 + 4i #complex
statement<-FALSE #logic
X
print(X)

```
```{r}
Y<-9 # not evaluated
```

## Integer sequence
```{r}
z<-1:10 #create a range 1 through 10
z
x <- seq(from=0, to=10, by=.5)
x
length(x)
summary(x)

```

##Vectors: the most basic object

A vector can only contain elements of the same class
```{r}
w<-c("name", "age", "gender")
x<-c("TRUE", "FALSE")
y<-c(1.5, 2.7)
z<-1:10

```
The function vector() creates a vector
```{r}
x<-vector("numeric", length = 4)
x
```
Index of a vector starts at 1 not 0
```{r}
x<-c(7,8,9)
x[1]
x[0] # numeric vector of length zero (i.e., empty)
```

##Implicit Coercion:

```{r}
x<-c(2.9, "b") # CHARACTER
class(x) 
y<-c(5, FALSE) # NUMERIC
class(y)
z<-c("b", TRUE) # CHARACTER
class(z)

```




class(X)
typeof(X)
